Time slice analyses

### 2017-09-20 analyses/02-time-slice-analyses.Rmd
Add details so code can be run when fixed

TITLE?
===============

DETAILS
This code loads the data and extracts matrices and other files needed to run the analyses in the paper. Note that these analyses can take time, so we save the outputs to a `data/backups` folder and use these in other `.Rmd` files so that the analyses can be replicated more quickly. Below we lay out the process in detail for one dataset, and then provide the code for the other datasets below this.

@@

Load packages
-----------------------------------

@@

```{r, eval = TRUE}
# The latest version of devtools and ape
library(devtools)
library(ape)

## The latest version of Claddis (on development on my own branch)
install_github("TGuillerme/Claddis")
library(Claddis)

## The latest version of dispRity 
install_github("TGuillerme/dispRity", ref = "release")
library(dispRity) 
```

@@

Stratigraphy
-----------------------------------

How to go about that????
Need to collate data ourselves or can we use strap?

```{r, eval = FALSE}

## Run the function for Beck data

slug <- "BeckLee"
metric <- c(sum, variances)
metric.name <- "sumvar"

for (bins in seq_along(c(5,10,15,20))){
 run.all.sims(morphospace, tree, FADLAD, bins, metric, 
              metric.name, inc.nodes = TRUE, slug)
}

slug <- "BeckLee"
metric <- c(median, centroids)
metric.name <- "medcentroid"

for (bins in seq_along(c(5,10,15,20))){
 run.all.sims(morphospace, tree, FADLAD, bins, metric, 
              metric.name, inc.nodes = TRUE, slug)
}

@@

>>>>

This code runs the analyses in the paper. Below we lay out the process in detail for one dataset, and then provide the code for the other datasets below this. Note that much of this uses functions in the `simulations.R` file.

@@

Load packages and functions
-----------------------------------

@@

```{r, eval = TRUE, message = FALSE}
# The latest version of devtools and ape
library(devtools)
library(ape)

## The latest version of Claddis (on development on TG branch)
## install_github("TGuillerme/Claddis")
library(Claddis)

## The latest version of dispRity on master branch
## install_github("TGuillerme/dispRity", ref = "master")
library(dispRity)

## Load functions using source
# Need to fix this!
# source("../functions/simulations_fun.R")
```

@@

Scenarios
--------------------------------

We used the data to explore these different scenarios:

1. Stratigraphy. This is the traditional method, where all the species within each stratigraphic period are included in the disparity calculation. This often leads to bins of unequal duration.

2. Equally sized time bins. 
    i. Where the *duration* of the bin is equal to the median duration of the stratigraphic period.
    ii. Where the *number* of bins is equal to the number of stratigraphic periods.
    iii. Where the *number* of bins is either 2, 5, 10, 15, or 20.

3. Time slicing. 
    i. Where the *interval* between slices is equal to the median duration of the stratigraphic period.
    ii. Where the *number* of slices is equal to the number of stratigraphic periods.
    iii. Where the *number* of slices is either 2, 5, 10, 15, or 20.

Running the analyses and saving the outputs
--------------------------------------------

These analyses use a series of functions in `functions\`. These essentially wrap the existing `dispRity` functions so that running lots of models and extracting lots of data is not such a big issue.

```{r, eval = FALSE, warning = FALSE}
## Run the function for Beck data
slug <- "BeckLee"

## Ages
out1 <- run.all.disparity.strat(morphospace, tree, type = "Age", FADLAD, inc.nodes = TRUE,
                                bootstraps = 100, metric = c(sum, variances), metric.name = sum_var)
readr::write_csv(out1, path = paste0("../outputs/age", "_", slug, ".csv"))

## Epochs
out2 <- run.all.disparity.strat(morphospace, tree, type = "Epoch", FADLAD, inc.nodes = TRUE,
                        bootstraps = 100, metric = c(sum, variances), metric.name = sum_var)
readr::write_csv(out2, path = paste0("../outputs/epoch", "_", slug, ".csv"))
```

We also ran the models using varying numbers of bins as follows.

```{r, eval = FALSE}
## Run the function for Beck data
slug <- "BeckLee"

for (bins in seq_along(c(2, 5, 10, 15, 20))){
  output <- run.all.disparity(morphospace, tree, bins, FADLAD, inc.nodes = TRUE,
                              bootstraps = 100, = c(sum, variances), metric.name = sum_var){

  readr::write_csv(output, path = paste0("../outputs/bins", "_", slug, ".csv"), append = TRUE)
}

@@

<!-- TG: Suggestion for a "testing the effect of binning/slicing" pipeline -->

Examining the output 
--------------------

Plots
Statistics
